The pollination trade-off

### 2018-11-24 paper/manuscript.Rmd
Do not need to define and call plot name
Improve looks of quant qual plot and move it to corresponding subsection

slopes_plot <- cowplot::plot_grid(
  right,
  left,
  ncol = 2,
  rel_widths = c(sum(rw[1:2]), sum(rw[3:4]))
)
slopes_plot
# dev.off()

# pdf(width = 3.25, height = 3)
# plot_bagged_vs_open_conspecific(dep_frame)
# dev.off()

@@

```{r fig-average-qual-quant, fig.height=1.5, fig.width=6.5, fig.cap="Mean relative effect of ecological variables on the quantity and quality of pollination. Results are shown for values calculated with both the absolute gain in pollen density (abs.) and the gain relative to selfing (rel.). Bootstrap confidence intervals of the mean (at the 0.05 level) are shown in square brackets. "}
# height1 <- 1.25
# height2 <- 1.65
# pdf(width = 3.25 * 2, height = 1.5)
# fig_coef_avg <- plot_coefficient_averages(coefficient_averages, variable_importance)
width_imp <- 1
mult <- 1.5
# fig_var_importance <- plot_variable_importance(variable_importance)
drake::loadd(fig_var_importance)
drake::loadd(fig_coef_avg)
cowplot::plot_grid(
  fig_var_importance[[1]],
  fig_var_importance[[2]],
  fig_coef_avg[[1]],
  fig_coef_avg[[2]],
  ncol = 4, 
  rel_widths = c(width_imp,width_imp, width_imp*mult, width_imp * mult * 1.45), 
  align = "h"
  )
# dev.off()
```

>>>>

cowplot::plot_grid(
  right,
  left,
  ncol = 2,
  rel_widths = c(sum(rw[1:2]), sum(rw[3:4]))
)

# dev.off()
```

# pdf(width = 3.25, height = 3)
# plot_bagged_vs_open_conspecific(dep_frame)
```{r fig-average-qual-quant, fig.height=1.29, fig.width=6.5, fig.cap="Mean relative effect of ecological variables on the quantity and quality of pollination. Results are shown for values calculated with both the absolute gain in pollen density (abs.) and the gain relative to selfing (rel.). Bootstrap confidence intervals of the mean (at the 0.05 level) are shown in square brackets."}
# height1 <- 1.25
# height2 <- 1.65
# pdf(width = 3.25 * 2, height = 1.29)
# fig_coef_avg <- plot_coefficient_averages(coefficient_averages, variable_importance)
width_imp <- 6.5/3
mult <- 2.125
width_coef_1 <- (6.5 - width_imp) / (1 + mult)
width_coef_2 <- 5.6 - width_imp - width_coef_1
# fig_var_importance <- plot_variable_importance(variable_importance)
drake::loadd(fig_var_importance)
drake::loadd(fig_coef_avg)
cowplot::plot_grid(
  fig_var_importance[[1]],
  fig_var_importance[[2]],
  fig_coef_avg[[1]],
  fig_coef_avg[[2]],
  ncol = 4, 
  rel_widths = c(width_imp/2, width_imp/2,width_coef_1, width_coef_2), 
  align = "h"
  )
# dev.off()
```

@@
